SST_patterns

### 2019-08-28 SST_patterns.Rmd
Updated the pixel finding pipeline to use purrr

```{r}
# Splitting the dataset

PN_site <- site_pixels %>% 
  filter(site == "Port Nolloth")

LB_site <- site_pixels %>% 
  filter(site == "Lamberts Bay")

SB_site <- site_pixels %>% 
  filter(site == "Saldanha Bay")

SP_site <- site_pixels %>% 
  filter(site == "Sea Point")

HB_site <- site_pixels %>% 
  filter(site == "Hout Bay")

## Functions:

MUR <- MUR %>% 
  select(site, lon, lat, temp.y)

OISST <- OISST %>% 
  select(site, lon, lat, temp.y)

unique_pixels <- function(df){
  unique_pixel <- df %>%
  select(lon, lat) %>%
  unique()
  return(unique_pixel)
}

MUR_pixels <- unique_pixels(df = MUR)
# SACTN_pixels <- unique_pixels(df = SACTN)
OISST_pixels <- unique_pixels(df = OISST)
CMC_pixels <- unique_pixels(df = CMC)

match_func <- function(df, xy){
  match_index <- knnx.index(data = as.matrix(df[,1:2]),
                    query = as.matrix(xy[,2:3]), k = 1)
  return(match_index)
}

MUR_PN <- match_func(df = MUR_pixels, xy = PN_site)
MUR_LB <- match_func(df = MUR_pixels, xy = LB_site)
MUR_SB <- match_func(df = MUR_pixels, xy = SB_site)
MUR_SP <- match_func(df = MUR_pixels, xy = SP_site)
MUR_HB <- match_func(df = MUR_pixels, xy = HB_site)

# SACTN_pixels <- match_func(df = SACTN)
OISST_PN <- match_func(df = OISST_pixels, xy = PN_site)
OISST_LB <- match_func(df = OISST_pixels, xy = LB_site)
OISST_SB <- match_func(df = OISST_pixels, xy = SB_site)
OISST_SP <- match_func(df = OISST_pixels, xy = SP_site)
OISST_HB <- match_func(df = OISST_pixels, xy = HB_site)

CMC_PN <- match_func(df = CMC_pixels, xy = PN_site)
CMC_LB <- match_func(df = CMC_pixels, xy = LB_site)
CMC_SB <- match_func(df = CMC_pixels, xy = SB_site)
CMC_SP <- match_func(df = CMC_pixels, xy = SP_site)
CMC_HB <- match_func(df = CMC_pixels, xy = HB_site)

pixel_match_func <- function(df, xy){ 
  pixel_match <- df[xy,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = PN_site$site)
  return(pixel_match)
}

MUR_match_PN <- pixel_match_func(df = MUR_pixels, xy = MUR_PN)
MUR_match_LB <- pixel_match_func(df = MUR_pixels, xy = MUR_LB)
MUR_match_SB <- pixel_match_func(df = MUR_pixels, xy = MUR_SB)
MUR_match_SP <- pixel_match_func(df = MUR_pixels, xy = MUR_SP)
MUR_match_HB <- pixel_match_func(df = MUR_pixels, xy = MUR_HB)

CMC_match_PN <- pixel_match_func(df = CMC_pixels, xy = CMC_PN)
CMC_match_LB <- pixel_match_func(df = CMC_pixels, xy = CMC_LB)
CMC_match_SB <- pixel_match_func(df = CMC_pixels, xy = CMC_SB)
CMC_match_SP <- pixel_match_func(df = CMC_pixels, xy = CMC_SP)
CMC_match_HB <- pixel_match_func(df = CMC_pixels, xy = CMC_HB)

OISST_match_PN <- pixel_match_func(df = OISST_pixels, xy = OISST_PN)
OISST_match_LB <- pixel_match_func(df = OISST_pixels, xy = OISST_LB)
OISST_match_SB <- pixel_match_func(df = OISST_pixels, xy = OISST_SB)
OISST_match_SP <- pixel_match_func(df = OISST_pixels, xy = OISST_SP)
OISST_match_HB <- pixel_match_func(df = OISST_pixels, xy = OISST_HB)

match_func <- function(df,xy){
matched_coords <- df %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% xy$combi)
return(matched_coords)
}

MUR_temp_PN <- match_func(df = MUR, xy = MUR_match_PN)
MUR_temp_LB <- match_func(df = MUR, xy = MUR_match_LB)
MUR_temp_SB <- match_func(df = MUR, xy = MUR_match_SB)
MUR_temp_SP <- match_func(df = MUR, xy = MUR_match_SP)
MUR_temp_HB <- match_func(df = MUR, xy = MUR_match_HB)

CMC_temp_PN <- match_func(df = CMC, xy = CMC_match_PN)
CMC_temp_LB <- match_func(df = CMC, xy = CMC_match_LB)
CMC_temp_SB <- match_func(df = CMC, xy = CMC_match_SB)
CMC_temp_SP <- match_func(df = CMC, xy = CMC_match_SP)
CMC_temp_HB <- match_func(df = CMC, xy = CMC_match_HB)
```

>>>>

```{r}

# RWS: It appears as though the satellite data you are loading here have already been trimmed down to the one nearest pixel to each SACTN site
# This won't work for the following steps because you need to be finding pixels from the COMPLETE set of satellite data you downloaded
# Once you load the complete satellite data lon/lat values you can run the following code and it should give you the coordinates you want

# These following three objects (MUR, OISST, CMC) need to be the complete set of lon/lat values for your satellite data
MUR <- MUR %>% 
  select(lon, lat) %>% 
  mutate(product = "MUR")

OISST <- OISST %>% 
  select(lon, lat) %>% 
  mutate(product = "OISST")

CMC <- CMC %>% 
  select(lon, lat) %>% 
  mutate(product = "CMC")

sat_data <- rbind(MUR, OISST) %>% 
  rbind(., CMC) %>% 
  select(product, lon, lat)

# rm(MUR, OISST, CMC); gc()

sat_pixels <- sat_data %>% 
  select(product, lon, lat) %>%
  unique()

## For testing the nest/map pipeline
# df <- sat_pixels %>% 
#   filter(product == "MUR", site == "Lamberts Bay") %>% 
#   select(-c(product, site))

match_func <- function(df){
  df <- na.omit(df) %>% 
    dplyr::rename(lon_sat = lon, lat_sat = lat)
  match_index <- knnx.index(data = as.matrix(site_pixels[,2:3]),
                    query = as.matrix(df[,1:2]), k = 1)
  res <- cbind(site_pixels[match_index,], df)
  return(res)
}

pixel_match <- sat_pixels %>% 
  group_by(product) %>% 
  nest() %>% 
  mutate(match = purrr:::map(data, match_func)) %>% 
  select(-data) %>%
  unnest(match)

# You may then use the 'pixel_match' object to filter out the desired pixels from the full satellite products
# You will then have one time series for each product for each pixel at each distance for each site that you may then
# run the upwelling event function on
# You should do this via purrr::nest+map as you can see how much less code it requires
```
